Our Title

### 2015-05-08 draft.tex
Added in new Chapter 6 - "Policy Response".

Initially, the Sunnis had a majority, with Abu Bakr assuming power as the first Caliph. Following the death of Abu Bakr in 634, two other Sunni Muslims were selected as the next two Caliphs \cite{schmidt2004great}. After decades of fighting and assassinations between these two early sects, Ali became Caliph in 656, but his reign was filled with great internal chaos. Following his death in 661, the reign passed on to his son, Hasan, ushering in centuries of expansion under the dynastic Caliphates, the Umayyad Caliphate (661–750), and Abbasid Caliphate (750–1517) \cite{schmidt2004great,oliver2009caliphate}. By 1517, the Abbasid Caliphate had its seat of power located in Cairo; when the Ottoman Empire annexed Cairo, the Ottomans usurped the office of the Caliph from that last Abbasid Caliph. This ushered in a period of even more rapid expansion under  the Ottoman Caliphate, which lasted until 1924, when Turkey abolished the Caliphate as part of secular and constitutional reform following the Treaty of Versailles of 1919 \cite{schmidt2004great,ozoglu2011caliphate}. The remainder of the Middle East was divided up into largely British and French protectorates, which remains as a point of grievance for many Muslims.

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.6]{./figures/current_territory.png}
   \caption{Current ISIL Territory \cite{BBC2015a}}
     \label{fig:current_territory2}
\end{figure}

@@

 \begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 5.9cm 0cm 5.35cm, clip,scale=0.6]{./figures/ISILRelationships.pdf}
   \caption{ISIL relationships as of mid-2014.  Note the figure uses the alternative name of ISIL that was preferred by the Obama administration for ISIL \cite{NationalConsortiumfortheStudyofTerrorismandResponsestoTerrorism2014}}
     \label{fig:ISILRelationships}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[scale=0.4]{./figures/affmap.png}
   \caption{Map of countries with ISIL affiliates \cite{IntelCenter2015}. }
     \label{fig:affmap}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[scale=0.6]{./figures/enablers.jpg}
   \caption{Flow of foreign fighters into Syria \cite{Thorp2014}. }
     \label{fig:enablers}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|}
\hline
\multicolumn{1}{|c|}{Material}                                              & Critical Mass, Bare Sphere (kg) & Fully Tampered Sphere (kg) \\ \hline
\ce{^{235}U}                                                                       & 52                              & 17                    \\ \hline
\ce{^{239}Pu} (alpha phase)                                                        & 10                              & 4                     \\ \hline
\ce{^{239}Pu} (delta phase)                                                        & 16                              & 6                     \\ \hline
\begin{tabular}[c]{@{}l@{}}Reactor Grade Pu \\(60\% enriched in \ce{^{239}Pu})\end{tabular} & 13                              & -                     \\ \hline
\ce{^{233}U}                                                                      & 15                              & 6                     \\ \hline
\end{tabular}
\caption{Critical Masses of a Bare and Fully Tampered Sphere for Various Special Nuclear Materials \cite{Moody2014} }
\label{tab:critical_mass}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Radiation Type}}                                                                                                       & \multicolumn{1}{c|}{\textbf{Quality Factor, Q}}              \\ \hline
Gamma rays, X-rays                                                                                                                                  & 1                                                            \\ \hline
Electrons, beta particles                                                                                                                           & 1                                                            \\ \hline
\begin{tabular}[c]{@{}l@{}}Neutrons:\\ \textless 10 keV\\ 10 keV to 100 keV\\ 100 keV to 2 MeV\\ 2 MeV to 20 MeV\\ \textgreater 20 MeV\end{tabular} & \begin{tabular}[c]{@{}l@{}}\ \\ 5\\ 10\\ 20\\ 10\\ 5\end{tabular} \\ \hline
Protons                                                                                                                                             & 10                                                           \\ \hline
Alpha particles, fission fragments, heavy ions                                                                                                      & 20                                                           \\ \hline
\end{tabular}
\caption{Quality factors for various types of radiation \cite{U.S.NuclearRegulatoryCommission2014}.}
\label{tab:quality_factors}
\end{table}

@@

\section{Fuel Cycle}

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|}
\hline
\textbf{Dose (rem)} & \textbf{Health Effect}           & \textbf{Time to Onset (without treatment)} \\ \hline
5-10                    & Changes in blood chemistry       & Hours                                      \\ \hline
50                      & Nausea                           & Hours                                      \\ \hline
55                      & Fatigue                          & Hours                                      \\ \hline
70                      & Vomiting                         & Hours                                      \\ \hline
75                      & Hair loss                        & 2-3 weeks                                  \\ \hline
90                      & Diarrhea                         & 2-3 weeks                                  \\ \hline
100                     & Hemorrhage                       & 2-3 weeks                                  \\ \hline
400                     & Possible death                   & Within 2 months                            \\ \hline
1,000                   & Destruction of intestinal lining & Within 2 months                            \\ \hline
1,000                   & Internal bleeding                & 1-2 weeks                                  \\ \hline
1,000                   & Death                            & 1-2 weeks                                  \\ \hline
2,000                   & Damage to central nervous system & 1-2 weeks                                  \\ \hline
2,000                   & Loss of consciousness            & Minutes                                    \\ \hline
2,000                   & Death                            & Hours to days                              \\ \hline
\end{tabular}
\caption[Deterministic health effects at various radiation doses \cite{USEPA1999}]{Deterministic health effects at various radiation doses \cite{USEPA1999} \footnotemark}
% \caption[Deterministic health effects at various radiation doses]{Deterministic health effects at various radiation doses \cite{USEPA1999} }
\label{tab:health_effects}
\end{table}

@@

\begin{table}[H]

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6]{./figures/assembly_methods.pdf}
  \caption{Schematic illustrations of gun-type and implosion devices \cite{WikimediaCommons2006}.}
  \label{fig:assembly_methods}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{./figures/Ulam_device.png}
  \caption{Schematic representation of the design of a fusion weapon \cite{WikimediaCommons2005}.}
  \label{fig:ulam_device}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{./figures/structure_infographic.jpg}
   \caption{Structure of the Office of the Director of National Intelligence \cite{OfficeoftheDirectorofNationalIntelligence}}
     \label{fig:structure_infographic}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{./figures/pu_signatures.png}
   \caption{The expected and measured ratio of isotopes of Plutonium, listed by facility of origin \cite{B412922A}.}
     \label{fig:pu_signatures}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.5]{./figures/shielding_reqs.jpg}
   \caption{Schematic representation of the shielding requirements of alpha, beta, and gamma radiation \cite{Hallenbeck1994}. }
     \label{fig:shielding_reqs}
\end{figure}

@@

\chapter{What can be done - possibilities for our policy to be implemented}

\section{Logic Trees}

Waiting on Julie

The logic tree can be seen in \autoref{fig:logic_tree}.

@@

>>>>

Initially, the Sunnis had a majority, with Abu Bakr assuming power as the first Caliph. Following the death of Abu Bakr in 634, two other Sunni Muslims were selected as the next two Caliphs \cite{schmidt2004great}. After decades of fighting and assassinations between these two early sects, Ali became Caliph in 656, but his reign was filled with great internal chaos. Following his death in 661, the reign passed on to his son, Hasan, ushering in centuries of expansion under the dynastic Caliphates, the Umayyad Caliphate (661-750), and Abbasid Caliphate (750-1517) \cite{schmidt2004great,oliver2009caliphate}. By 1517, the Abbasid Caliphate had its seat of power located in Cairo; when the Ottoman Empire annexed Cairo, the Ottomans usurped the office of the Caliph from that last Abbasid Caliph. This ushered in a period of even more rapid expansion under  the Ottoman Caliphate, which lasted until 1924, when Turkey abolished the Caliphate as part of secular and constitutional reform following the Treaty of Versailles of 1919 \cite{schmidt2004great,ozoglu2011caliphate}. The remainder of the Middle East was divided up into largely British and French protectorates, which remains as a point of grievance for many Muslims.

@@

\begin{figure}
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.6]{./figures/current_territory.png}
   \caption{Current ISIL Territory \cite{BBC2015a}}
     \label{fig:current_territory2}
\end{figure}

@@

 \begin{figure}
 \centering
 \includegraphics[trim = 0cm 5.9cm 0cm 5.35cm, clip,scale=0.6]{./figures/ISILRelationships.pdf}
   \caption{ISIL relationships as of mid-2014.  Note the figure uses the alternative name of ISIL that was preferred by the Obama administration for ISIL \cite{NationalConsortiumfortheStudyofTerrorismandResponsestoTerrorism2014}}
     \label{fig:ISILRelationships}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[scale=0.4]{./figures/affmap.png}
   \caption{Map of countries with ISIL affiliates \cite{IntelCenter2015}. }
     \label{fig:affmap}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/enablers.jpg}
   \caption{Flow of foreign fighters into Syria \cite{Thorp2014}. }
     \label{fig:enablers}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{|l|c|c|}
\hline
\multicolumn{1}{|c|}{Material}                                              & Critical Mass, Bare Sphere (kg) & Fully Tampered Sphere (kg) \\ \hline
\ce{^{235}U}                                                                       & 52                              & 17                    \\ \hline
\ce{^{239}Pu} (alpha phase)                                                        & 10                              & 4                     \\ \hline
\ce{^{239}Pu} (delta phase)                                                        & 16                              & 6                     \\ \hline
\begin{tabular}[c]{@{}l@{}}Reactor Grade Pu \\(60\% enriched in \ce{^{239}Pu})\end{tabular} & 13                              & -                     \\ \hline
\ce{^{233}U}                                                                      & 15                              & 6                     \\ \hline
\end{tabular}
\caption{Critical Masses of a Bare and Fully Tampered Sphere for Various Special Nuclear Materials \cite{Moody2014} }
\label{tab:critical_mass}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Radiation Type}}                                                                                                       & \multicolumn{1}{c|}{\textbf{Quality Factor, Q}}              \\ \hline
Gamma rays, X-rays                                                                                                                                  & 1                                                            \\ \hline
Electrons, beta particles                                                                                                                           & 1                                                            \\ \hline
\begin{tabular}[c]{@{}l@{}}Neutrons:\\ \textless 10 keV\\ 10 keV to 100 keV\\ 100 keV to 2 MeV\\ 2 MeV to 20 MeV\\ \textgreater 20 MeV\end{tabular} & \begin{tabular}[c]{@{}l@{}}\ \\ 5\\ 10\\ 20\\ 10\\ 5\end{tabular} \\ \hline
Protons                                                                                                                                             & 10                                                           \\ \hline
Alpha particles, fission fragments, heavy ions                                                                                                      & 20                                                           \\ \hline
\end{tabular}
\caption{Quality factors for various types of radiation \cite{U.S.NuclearRegulatoryCommission2014}.}
\label{tab:quality_factors}
\end{table}

@@

\section{Fuel Cycle} \label{sec:fuel_cycle}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
\textbf{Dose (rem)} & \textbf{Health Effect}           & \textbf{Time to Onset (without treatment)} \\ \hline
5-10                    & Changes in blood chemistry       & Hours                                      \\ \hline
50                      & Nausea                           & Hours                                      \\ \hline
55                      & Fatigue                          & Hours                                      \\ \hline
70                      & Vomiting                         & Hours                                      \\ \hline
75                      & Hair loss                        & 2-3 weeks                                  \\ \hline
90                      & Diarrhea                         & 2-3 weeks                                  \\ \hline
100                     & Hemorrhage                       & 2-3 weeks                                  \\ \hline
400                     & Possible death                   & Within 2 months                            \\ \hline
1,000                   & Destruction of intestinal lining & Within 2 months                            \\ \hline
1,000                   & Internal bleeding                & 1-2 weeks                                  \\ \hline
1,000                   & Death                            & 1-2 weeks                                  \\ \hline
2,000                   & Damage to central nervous system & 1-2 weeks                                  \\ \hline
2,000                   & Loss of consciousness            & Minutes                                    \\ \hline
2,000                   & Death                            & Hours to days                              \\ \hline
\end{tabular}
\caption[Deterministic health effects at various radiation doses \cite{USEPA1999}]{Deterministic health effects at various radiation doses \cite{USEPA1999} \footnotemark}
% \caption[Deterministic health effects at various radiation doses]{Deterministic health effects at various radiation doses \cite{USEPA1999} }
\label{tab:health_effects}
\end{table}

@@

\begin{table}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.6]{./figures/assembly_methods.pdf}
  \caption{Schematic illustrations of gun-type and implosion devices \cite{WikimediaCommons2006}.}
  \label{fig:assembly_methods}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{./figures/Ulam_device.png}
  \caption{Schematic representation of the design of a fusion weapon \cite{WikimediaCommons2005}.}
  \label{fig:ulam_device}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{./figures/structure_infographic.jpg}
   \caption{Structure of the Office of the Director of National Intelligence \cite{OfficeoftheDirectorofNationalIntelligence}}
     \label{fig:structure_infographic}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{./figures/pu_signatures.png}
   \caption{The expected and measured ratio of isotopes of Plutonium, listed by facility of origin \cite{B412922A}.}
     \label{fig:pu_signatures}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.5]{./figures/shielding_reqs.jpg}
   \caption{Schematic representation of the shielding requirements of alpha, beta, and gamma radiation \cite{Hallenbeck1994}. }
     \label{fig:shielding_reqs}
\end{figure}

@@

\chapter{Policy Response}

\section{Overview}

In attempting to prevent the acquisition of nuclear material, first and foremost the U.S. should continue this administration's declaratory policy: \enquote{our objective is clear: We will degrade, and ultimately destroy, ISIL through a comprehensive and sustained counterterrorism strategy} \cite{Hudson2014}.  The policy recommendations outlined below are meant to build on, not replace, the current efforts at defeating ISIL. Recommendations are listed in order of priority, based both on ease of implementation and effectiveness at preventing ISIL from obtaining a nuclear device.

\subsection{??????? ORDERED LIST OF RECOMMENDATIONS HERE ????????}

These recommendations were developed by modeling the steps ISIL would have to take to procure a nuclear device, from the inception of the idea, to staging and detonation. Each recommendation is meant to target a specific chain of this logic model, with the ultimate goal of destroying all paths ISIL may have to a nuclear device. The logic model is shown in \autoref{fig:logic_tree}, with different nodes highlighted to represent the level of risk to the U.S., with green cells being high risk, orange medium, and red low.

@@

\section{Coordinating Government Efforts to Counter Nuclear Terrorism}

\subsection{Putting Someone in Charge}

A key step for the United States in preventing ISIL acquisition and use of a nuclear device is to coordinate and organize the various initiatives across the government that are handling various pieces of this puzzle. In 2008, the authors of a Belfer Center report on preventing nuclear terrorism recommended that President Obama appoint a senior figure to a post in the National Security Council (suggesting this may be a new Deputy National Security Advisor) with the sole responsibility of waking up every morning and thinking about how to prevent a nuclear terrorist attack \cite{Bronner2008}. Since that time, President Obama created a new White House post called the White House Coordinator for Defense Policy, Countering Weapons of Mass Destruction, and Arms Control. The National Security Staff's former Senior Director for Europe, Liz Sherwood-Randall was promoted to that position \cite{Rogin2013}. While this is a step in the right direction, the arms-control role of this position is likely to consume much of Ms. Sherwood-Randall's time, forcing her to put some anti-nuclear terrorism initiatives on the backburner. For this reason, the authors of this report recommend that the White House:

\begin{itemize}
 \item Break out the countering nuclear terrorism aspect of the role of White House Coordinator for Defense Policy, Countering Weapons of Mass Destruction, and Arms Control, and create a new White House role within the National Security Council that deals exclusively with nuclear terrorism. 
 \item Limit the responsibilities of this role to nuclear terrorism, leaving out nuclear weapons concerns as related to Pakistan, North Korea, and Iran, as well as arms-control. These concerns would dominate much of this person's time, detracting from the necessary focus on preventing nuclear terrorism.
 \item Fill this position with a senior figure who commands respect across cabinet departments, and is capable of speaking on behalf of the president.
\end{itemize}

This person would have full responsibility for coordinating and overseeing counter-nuclear terrorism efforts. Making this role a Deputy National Security Advisor would have the advantage of giving the role the authority to integrate policies across the Department of Defense, the Department of Energy, the State Department, the Intelligence community, Homeland Security, and law enforcement \cite{Bronner2008}. This person would also have a role working with the Office of Management and Budget (OMB) to ensure that all agency budgets are aligned with the strategy they articulate. Additionally, the President can direct OMB to prepare a crosscut of departmental budgets to find all funds associated with preventing nuclear terrorism and put them under a single budget examiner \cite{Bronner2008}.

The above suggestions are consisted with the 2008 report from the Belfer Center. The report also emphasizes the importance of limiting the scope of this proposed role. In particular, this person should not be responsible to Pakistan, Iran, or North Korea, because these issues would take up all of this person's time \cite{Sharp2008}. This is the key problem with the current National Security Council role occupied by Ms. Sherwood-Randall - with arms control and broader counterterrorism efforts under her purview, there is still need for a senior official at this level in the White House dedicated exclusively to preventing nuclear terrorism.

Finally, this person should have a small staff that will help him or her put into place a comprehensive, prioritized plan to combat nuclear terrorism. This person will drive the government-wide efforts to prevent ISIL acquisition and use of a nuclear device.

\subsection{Creating an Interagency Group}

It will also be important for the White House to create a deputies committee focused on nuclear terrorism, led by the proposed Deputy Nuclear Security Advisor for Countering Nuclear Terrorism and including deputies with sole responsibility and departmental oversight of counter-nuclear terrorism from DoD, DoE, the State Department, Homeland Security, and law enforcement \cite{Bronner2008}.

Additionally, current efforts within departments remain split into various lower-level groups. In order to increase the effectiveness of department efforts and the implementation of the deputies committee, the White House should direct the Department of Energy, the Department of Defense, the State Department, and Homeland Security to have on official presiding over efforts to prevent nuclear terrorism.

\subsection{Articulating Priorities}

Another White House priority should be to articulate the central importance of combating ISIL efforts to acquire and use nuclear weapons. Creating a high-level Nuclear Security Council position is the beginning of demonstrating counter-nuclear terrorism as a United States priority and broadcasting this commitment to the international community.

In order to deal specifically with the ISIL threat, the White House should designate a focus on ISIL as a responsibility of the suggested Deputy National Security Advisor. The White House may also want to seek from Congress an appropriation to be available until expended on high-priority actions that will reduce the risk of nuclear theft and smuggling \cite{Bronner2008}. While articulating the request for the appropriation, the White House should focus on outlining the ISIL threat, and the ways in which the money could be spent that will cut down on the chances of ISIL acquiring a nuclear weapon - while reducing risk of other terrorist groups obtaining a nuclear weapon simultaneously.

\subsection{Build International Consensus}

In addition to taking the actions outlined above, the United States should launch a global security campaign aimed at building consensus that steps must be taken to reduce the risk of nuclear terrorism, encouraging allies and other nuclear powers to create high-level positions (similar to the proposed Deputy National Security Advisor), and coordinating state efforts to combat nuclear terrorism.

\subsection{??????????? This ref is never used! ???????????}

[4] Charles D. Ferguson, “Preventing Catastrophic Nuclear Terrorism,” Council on Foreign Relations. CSR No. 11, March 2006. \url{http://www.cfr.org/weapons-of-mass-destruction/preventing-catastrophic-nuclear-terrorism/p10067 }

\section{Fundamental Efforts}

There are three approaches to disrupting ISIL operations that will be particularly important in ensuring that ISIL does not acquire a nuclear device:

\begin{itemize}
 \item Disrupt ISIL cash flow
 \item Restrict ISIL access to nuclear weapons experts
 \item Rollback ISIL territorial gains
\end{itemize}

\subsection{Disrupt Cash Flow}

\bfseries Targeted Capability: Resources

Pathway: Money

Policy: Target ISIL Income Stream Proposed Policy: \textcolor{red}{Strengthen financial constraints and re-evaluate targeting}

\subsubsection{????????? Proposed Policy missing ??????????}

Proposed Policy: \textcolor{red}{???}

Lead Agency: Department of the Treasury

Contributing Agency: Intelligence Community \normalfont

ISIL's principal source of cash flow comes from the control and sale of oil, which brings in about \$1 million a day. ISIL is also financed through kidnappings, extortion, criminal activities, and a small amount from external donations \cite{Lister2014}. ISIL employs roughly 30,000 fighters, including 19,000 foreign fighters from 90 different countries, paying them roughly \$350-\$500 a month. This comes out to \$10 million per month. ISIL also recruits fighters in the region by providing electricity and other services to local residents \cite{TheEditorialBoard2015}. A new report by Financial Action Task Force (FATF) finds that it is unclear whether ISIL's revenue collection will be sustainable over time, and that ISIL will have to gain more territory to remain financially viable \cite{TheEditorialBoard2015,Report2015}.

The Department of Treasury (DoT) has prepared a strategy to disrupt ISIL's revenue streams by targeting sanctions, cutting off cross-border oil smuggling, and refusing to pay ransoms for kidnappings \cite{Cohen2014}. In undermining the group's ability to generate revenue, these steps will also slow or halt ISIL's potential WMD acquisition process by reducing the funds available to ISIL to purchase a bomb or fissile material, create an indigenous capability, recruit nuclear scientists, or make territorial gains that could give them access to sensitive facilities. The DoT strategy is to:

\begin{enumerate}
 \item Disrupt revenue streams
 \item Restrict access to international financial systems
 \item Target leaders and supporters with sanctions
\end{enumerate}

We believe DoT's approach to degrading ISIL's financing is the most effective available route, and that disrupting finances through targeted sanctions remains a strength of the broader U.S. approach to ISIL. Our primary recommendation is that DoT continues with the path it has staked out to degrade ISIL finances. In addition to holding to the current playbook, we propose several small recommendations that may help to advance DoT's efforts:

\begin{itemize}
 \item The United States should evaluate the viability of phasing away from targeting oil fields for air strikes, and instead target ISIL's transportation and sale of oil, in order to preserve oil infrastructure for civilians in ISIL control areas, which we anticipate will weaken ISIL's recruiting efforts by mitigating anti-American sentiment \cite{Lister2014}.
 \item In aiding opposition groups in northern Syria, the United States should provide large quantities of diesel fuel and oil for generators in the areas controlled by these groups \cite{Lister2014}.
 \item The State Department and U.S. Embassies should continue to work with Kuwait and Qatar, along with other government in the region, to create and strengthen legislation that counters financing of ISIL's efforts \cite{Lister2014}.
 \item The State Department should provide incentives to the cyber security and reconnaissance and surveillance industry to continually provide the intelligence community with information about ISIL activities.
\end{itemize}

\subsubsection{Disrupt Revenue Streams}

DoT has stated that it will impose targeted sanctions on anyone who purchases ISIL oil. Additionally, DoT is working to identify middlemen, refiners, transporters, and everyone else in the supply chain \cite{Cohen2014}. Beyond sanctions, DoT is working to stem cross-border oil smuggling, in collaboration with others in the U.S. government as well as Turkish and Iraqi Kurdish authorities \cite{Cohen2014}.

Crippling ISIL oil revenue, however, is likely more complicated than it might seem. ISIL has been working to establish an internal market for their oil by providing cheap oil to the people in the territories they control, and by using it to fuel their own fleets \cite{Lister2014}. Some of the major U.S. airstrikes have targeted oil fields, but this also cuts off oil supplies for Syrian rebels and civilians in the region. This has been a central complaint of Syrian rebels, who lament that airstrikes disrupt oil supply to power generators and local facilities, allowing ISIL to pass the blame on to the United States. The United States should evaluate the viability of phasing away from targeting oil fields for strikes, and instead targeting ISIL's transportation and sale of oil. This approach may be made more viable by intelligence generated by DoT's efforts to identify everyone in the ISIL oil supply chain.

\subsubsection{?????? Need justification for the claim below ?????????}

In the meantime, the United States should provide large quantities of diesel fuel and oil for generators in opposition areas of northern Syria \cite{Lister2014}.

In the current oil market, diminished profits from selling oil may make ISIL more dependent on external donations. As need for this arises, it is important to focus now on these external sources. DoT has worked to choke-off key smuggling routes, and good work has been done in Saudi Arabia and UAE to crack down on ISIL oil sales there. However, while Kuwait and Qatar have passed legislation to counter financing of ISIL and other terrorist groups, both countries remain too permissive of ISIL oil sales and other forms of terrorist funding. More needs to be done by these states to enforce their newly passed laws against financing terrorism, and the United States should reach out to these states via the State department and U.S. embassies in order to make sure that these states are cracking down on terrorist funding. Diplomacy of this type promises mutual gains, since both Kuwait and Qatar have an interest in stopping ISIL, which has periodically targeted Qatar and its Ministry of Foreign Affairs \cite{Lister2014}.

Extortion and illicit taxation are large, internally sustainable methods of funding for ISIL. Before capturing Mosul, ISIL was already earning \$12 million a month in the city from these methods. A sophisticated ISIL taxation system has been created in on the main highway between Jordan and Baghdad that replaces the government's import tax by charging a reduced rate for goods transported into the capital. ISIL does this throughout Iraq and Syria, and ensures its survivability by gaining tax income while charging low rates to Sunni truckers and other Sunnis to curry favor. Truly eroding this source of funding means breaking ISIL's hold over the territory. This is highly unlikely to happen without sophisticated ground forces following up on the airstrikes. This will be discussed in greater depth in the section on rolling back ISIL's territorial gains \cite{Lister2014}.

Another source of ISIL funding is social media fundraising. The group has demonstrated the ability to engage in complex online fundraising activities; ISIL even uses \enquote{tiered} donations common to crowdfunding sites in which donors get various perks and special thank-you messages depending on their level of donation \cite{Report2015}.

\subsubsection{?????  What does this stand for ????????}

BAE systems and other surveillance and reconnaissance companies have mapped ISIL's social network by data mining to collect information from social media accounts linked to ISIL \cite{Tadjdeh2014}. These companies and others should be incentivized to continue to gather information on ISIL's efforts and to scour the Internet for threats, including identity and intellectual property theft. The State Department can support these efforts by providing incentives to the industry to provide the U.S. government with information about ISIL activities. A final recommendation is to put more of the government's own intelligence resources toward detecting ISIL social media fundraising efforts \cite{Report2015}.

\subsubsection{Restrict ISIL access to international financial systems}

Operating entirely in cash is risky and cumbersome, and it will be important for ISIL to access the banking system in Syria, Iraq, and internationally. Access to the international banking system is also important for ISIL to fund external operations, including operatives who may be tasked with attacking the U.S. homeland. DoT is aiming to prevent ISIL from using bank branches in the territory where ISIL operates, as well as the international banking system as a whole \cite{Cohen2014}. The private sector is also important in these efforts. The Bank Secrecy Act allows private companies to give DoT insight into financial activity in areas where ISIL operates \cite{Cohen2014}. DoT efforts in this area are strong and should continue.

\subsubsection{Target ISIL leaders and supporters with sanctions}

DoT has engaged in extensive efforts to target ISIL leaders and supporters with sanctions, and has indicated that will continue to rely on new intelligence to continue to expand the scope of its sanctions \cite{Cohen2014}. In particular, DoT sanctions against the CFO-like figures who manage ISIL funding networks will disrupt the group's ability to raise money and recruit fighters. In addition to DoT's current actions, the FATF report suggests that the U.S. government should encourage other countries to proactively identify individuals and entities for inclusion in the UN al-Qaeda Sanctions Committee list \cite{Report2015}. DoT efforts are strong in this area as well, and our recommendation is that DoT continue down its current path.

\subsection{Restrict ISIL access to nuclear weapons experts}

\bfseries Targeted Capability: Resources

Pathway: People

Policy: \textcolor{red}{Limiting passports, continual surveillance, and combatting propaganda}

Proposed Policy: \textcolor{red}{Renew funding for Expanded Threat Reduction Initiative}

Lead Agency: National Security Agency

Contributing Agency: Intelligence Community and Department of State \normalfont

Nuclear scientists and others with access to sensitive nuclear materials, facilities, or knowledge might chose to support ISIL for two key reasons, monetary and ideological.

In order to reduce the risk that nuclear scientists and others with access to sensitive facilities, materials or knowledge pose, the United States should:

\begin{itemize}
 \item Use the architecture of the Expanded Threat Reduction Initiative (ETR) of the Clinton Administration to fund employment and research for nuclear scientists through the State Department. 
 \item Continue to combat ISIL propaganda with media outreach, in order to lessen support for the group that may spread to nuclear scientists.
\end{itemize}

In order to reduce monetary incentives for scientists to join ISIL, the most effective measure is to ensure that nuclear scientists have steady employment and research opportunities. A Congressional Research Report for Congress from 1999 (obtained by WikiLeaks) spells out the Clinton administration's approach to this problem by evaluating the administration's budget request from \$4.5 billion over 5 years for the Expanded Threat Reduction Initiative (ETR) \cite{Woolf1999}. In the report, Amy Woolf and Curt Tarnoff described the steps proposed in the budget request:

\blockquote{Over the next five years, planned spending would increase from \$2.7 billion to \$4.5 billion. The added funds would not only augment ongoing programs to secure nuclear, chemical, and biological weapons and materials, it would also expand programs that focus on keeping scientists and engineers away from rogue nations \ldots

\ldots The State Department manages several programs that offer NIS scientists employment and research opportunities, so that they will be less likely to sell their knowledge to rogue nations. The International Science and Technology Center (ISTC) in Moscow and the Science and Technology Center in Ukraine (STCU), multilateral programs supported by the EU, Japan, and others, fund research in such areas as nuclear reactor safety, medicine, civil aviation, and energy production. A \enquote{Partners Program} links NIS scientists with contributing U.S. private sector companies, such as General Electric and Lockheed Martin, and academic institutes to assist their own R\&D efforts. The Civilian Research and Development Foundation (CRDF) is a private, non-profit foundation, originally funded by matching grants from DOD and George Soros. It supports U.S. collaboration and exchanges with former NIS defense scientists on civilian basic and applied research, and supports projects with commercial applications. The State Department also implements a pilot project for biological weapons scientists to \enquote{redirect} their expertise toward commercial endeavors. Among other activities, it has established a collaborative program between the Department of Agriculture's Agricultural Research Service and Russian scientists on agriculture research, and between the Department of Health and Human Services' Centers for Disease Control, National Institutes of Health, and Food and Drug Administration and Russian biomedical scientists to conduct research on infectious diseases. }

The CRS report details that the FY2000 budget request for State Department efforts to employ scientists was \$146.5 million \cite{Woolf1999}. The authors of this report were unable to uncover up-to-date information on these efforts as they stand in regard to ISIL. It remains important, however, that the State Department finds ways to employ not only scientists, but also guards and other employees of nuclear facilities. The authors of this report do not have adequate information to calculate the budget necessary to revamp efforts to provide employment to the world's nuclear scientists, but the Clinton administration budget request from FY2000 may be a reliable benchmark for the costs of these types of programs.

In terms of the second threat - that nuclear scientists will seek to aid ISIL for ideological reasons - requires knowledge about the activities and communications of nuclear scientists. This work will occur through the intelligence community, and should be made a priority in light of the seriousness of threat of a nuclear armed ISIL. The United States can also mitigate the risks of nuclear scientists collaborating with ISIL by continuing its current efforts to degrade the global reputation of ISIL \cite{Gearan2014}.

\subsection{Rollback ISIL territorial gains}

\bfseries Targeted Capability: Resources

Pathway: Land

\subsubsection{?????????  Policy missing ??????????}

Policy: \textcolor{red}{SUMMARY POLICY HERE}

\subsubsection{????????? Proposed Policy missing ??????????}

Proposed Policy: \textcolor{red}{SUMMARY POLICY HERE}

Lead Agency: Department of Defense

Contributing Agency: Intelligence Community \normalfont

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.6]{./figures/current_territory.png}
   \caption{Current ISIL Territory \cite{BBC2015a}}
     \label{fig:current_territory}
\end{figure}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{./figures/current2.png}
   \caption{What ISIL Wants \cite{Lewis2014}}
     \label{fig:current2}
\end{figure}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.4]{./figures/oil_reserves.png}
   \caption{Oil Reserves and Ground Transportation Routes \cite{PoliticalCalculations2012}}
     \label{fig:oil_reserves}
\end{figure}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{./figures/oil_infrastructure.jpg}
   \caption{Iraq's Oil \& Gas Infrastructure \cite{EnergyPolicyInformationCenter2014}}
     \label{fig:oil_infrastructure}
\end{figure}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.3]{./figures/minerals2.png}
   \caption{Mineral Deposits and Industry in Iraq, with current ISIL territory overlay \cite{Ellis2005}}
     \label{fig:minerals}
\end{figure}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.3]{./figures/elec_grid2.png}
   \caption{Iraqi Electricity Grid, with current ISIL territory overlay \cite{GlobalEnergyNetworkInstitute}}
     \label{fig:elec_grid}
\end{figure}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.6]{./figures/nuke_facilities2.png}
   \caption{Iraq Declared Nuclear Facilities (as of 2002), with current ISIL territory overlay \cite{Fox2002}}
     \label{fig:nuke_facilities}
\end{figure}
